### 2012-06-19 inst/examples/value_of_information.Rmd
restore original value_of_information (without all-negative growth shocks)

**quick debug check -- make z_g shocks only negative to confirm growth noise isn't good**

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() min(rlnorm(1,  0, true_g), 1)
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)

>>>>

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rlnorm(1,  0, true_g)
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)
